\documentclass[runningheads]{llncs}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{appendix}
% If you use the hyperref package, please uncomment the following two lines
% to display URLs in blue roman font according to Springer's eBook style:
%\usepackage{color}
%\renewcommand\UrlFont{\color{blue}\rmfamily}
%

% jiayuan for math and algorithm
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{algorithm}  % for algorithms
\usepackage{algorithmic}

% bo added. figure pos
% \usepackage{float}

\begin{document}
%
\title{CS6216 Project Report: \\Stein Variational Gradient Descent}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Apivich Hemachandra\inst{1}\orcidID{0000-1111-2222-3333} \and
Jiashu Tao\inst{1}\orcidID{A0159714X} \and
Bo Wang\inst{1}\orcidID{A0219236E}   \and
Jiayuan Ye\inst{1} }
%
%\authorrunning{F. Author et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{School of Computing, National University of Singapore, Singapore\\{\small\textsuperscript{*}Alphabetical Order.}}


\maketitle              % typeset the header of the contribution
%

\input{report/sections/abstract}
\input{report/sections/introduction}
\input{report/sections/summary}
\input{report/sections/experiments}
\input{report/sections/conclusion}

%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
% \bibliographystyle{splncs04}
% \bibliography{mybibliography}
%
\begin{thebibliography}{8}
\bibitem{ref_article_svgd}
Liu, Q., Wang, D. (2016). Stein variational gradient descent: A general purpose bayesian inference algorithm. Advances in neural information processing systems, 29.

\bibitem{ref_sgld}
Welling, M., Teh, Y. W. (2011). Bayesian learning via stochastic gradient Langevin dynamics. In Proceedings of the 28th international conference on machine learning (ICML-11) (pp. 681-688).

\bibitem{ref_dsvi}
Titsias, M., Lázaro-Gredilla, M. (2014, June). Doubly stochastic variational Bayes for non-conjugate inference. In International conference on machine learning (pp. 1971-1979). PMLR.

\bibitem{nuts}
M. D. Hoffman and A. Gelman. The No-U-Turn sampler: Adaptively setting path lengths in Hamiltonian Monte Carlo. The Journal of Machine Learning Research, 15(1):1593–1623, 2014.
\end{thebibliography}

\appendix
\input{report/sections/contrib}
\input{report/sections/appendix_code}
\end{document}
